---
title: "506hw3"
format: pdf
editor: visual
---

## Problem2

##a

```{r}
##install.packages("DBI")
library(DBI)
##install.packages("RSQLite")
library(RSQLite)
sakila <- dbConnect(RSQLite::SQLite(), "~/Downloads/sakila_master.db")
##dbListTables(sakila)
```

##a

```{r}
dbGetQuery(sakila,"SELECT language_id, COUNT(*) as film_count
FROM film
GROUP BY language_id
ORDER BY film_count DESC
LIMIT 1 OFFSET 1")
```

##b

```{r}
cate<-dbGetQuery(sakila, "SELECT category_id
FROM film_category")
catname<-dbGetQuery(sakila, "SELECT * from category")

count=c()
for(i in 1:16){
  count[i]=sum(cate==i)
}

id<-which.max(count)
catname$name[catname$category_id==id]
count[which.max(count)]
```

```{r}
dbGetQuery(sakila, "SELECT category.name as genre, COUNT (*) as cat_count
FROM film_category
JOIN category ON film_category.category_id=category.category_id
GROUP BY genre
ORDER BY cat_count DESC
Limit 1")
```

##c

```{r}

```

```{r}
dbGetQuery(sakila, "SELECT country, COUNT(customer_id) as cust_count
FROM customer
JOIN address ON customer.address_id = address.address_id
JOIN city ON address.city_id = city.city_id
JOIN country ON city.country_id = country.country_id
GROUP BY country
HAVING cust_count = 9")

```

## Problem3

```{r}
library(readr)
us_500 <- read_csv("~/Downloads/us-500.csv", show_col_types = FALSE)
##View(us_500)
```

##a

```{r}
pat<-"\\.net"
li<-grep(pat,us_500$email)
length(li)/length(us_500$email)
```

##b

```{r}
pat1<-"[^A-za-z0-9@]"
lis<-grep(pat1,us_500$email)
length(lis)/length(us_500$email)
```

##c

```{r}
##install.packages("stringr")
library(stringr)
```

```{r}
phonenum<-c(us_500$phone1,us_500$phone2)
areacode<-str_extract(phonenum,"[0-9]{3}")
code_count<-table(areacode)
names(table(areacode))[which.max(code_count)]
```

##d

```{r}
apnum<-str_extract(us_500$address,"#(\\d*)$")
apnum1<-stnum[!is.na(apnum)]
apnum2<-gsub("#", "", apnum1)
apnum3<-log(as.numeric(apnum2))
hist(apnum3, main = "Histogram of Log Apartment Numbers", xlab = "Log Apartment Numbers")
```

##e

```{r}
library(dplyr)
leading_digit<-as.numeric(substr(apnum2,1,1))

count<-c()
for(i in 1:9){
  count[i]=sum(leading_digit==i)/length(leading_digit)
}

count
```

We can observe that the the apartment number does not follow the Benford's law, since the probability distribution deviates from the expected one in the Benford's law. However, we can not make a definite conclusion that the apartment number is not real data based on the Benford's law analysis. Additional analysis is needed to draw a conclusion.

##f

```{r}
stnum<-str_extract(us_500$address,"^(\\d*)")
last_digit<-str_extract(stnum,"\\d$")

count<-c()
for(i in 1:9){
  count[i]=sum(last_digit==i)/length(last_digit)
}

count
```

We can observe that the the street number does not follow the Benford's law, since the probability distribution deviates from the expected one in the Benford's law.
